Appendix S1: Supporting Tables and Figures

### 2022-04-18 ms/SI.Rmd
Update MS
according to editor's comments

Phylogenetic endemism of the ferns of Japan measured using CANAPE (categorical analysis of neo- and paleo-endemism), restricted dataset including only taxa endemic to Japan. 'neo' indicates neodendemic areas (those with an overabundance of short branches); 'paleo' indicates paleoendemic areas (those with an overabundance of long branches); 'mixed' indicates significantly endemic sites that have neither an overabundance of short nor long branches; 'super' indicates highly significantly endemic sites that have neither an overabundance of short nor long branches. For details, see Materials and Methods.

@@

Scatterplots of grid cell membership in (A) taxonomic or (B) phylogenetic bioregions arranged by mean annual temperature and annual precipitation. Points shown with partial transparency; darker areas indicate overlapping points. Bioregions not consisting of more than `r english2(bioregion_cutoff)` grid-cells each are lumped into the "Other" category.

@@

Maps showing overlap of grid-cells with significantly high biodiversity for the ferns of Japan and protected areas. Grid-cells with black outlines indicate significantly high biodiversity. Biodiversity metrics include (A) taxon richness, (B) phylogenetic diversity (PD), (C) functional diversity (FD), and (D) phylogenetic endemism (PE). Significance of PD, FD, and PE assessed by a one-tailed test comparing observed values to a null distribution of 999 random values; for richness, grid-cells in the top 5% considered highly diverse (see Materials and Methods).

@@

Maps showing overlap of grid-cells with significantly high biodiversity for the ferns of Japan and distribution of Japanese deer (*Cervus nippon*). Grid-cells with black outlines indicate significantly high biodiversity. Biodiversity metrics include (A) taxon richness, (B) phylogenetic diversity (PD), (C) functional diversity (FD), and (D) phylogenetic endemism (PE). Significance of PD, FD, and PE assessed by a one-tailed test comparing observed values to a null distribution of 999 random values; for richness, grid-cells in the top 5% considered highly diverse (see Materials and Methods). Deer range data sources include 1978 survey, 2003 survey, and range estimated from model based on 2003 survey data. Deer ranges plotted in layers in ascending order (estimated, 2003, 1978) such that upper layers may obscure lower layers; however, deer ranges generally expanded from 1978 to estimated range, so very few sites are obscured.

>>>>

Phylogenetic endemism of the ferns of Japan measured using CANAPE (categorical analysis of neo- and paleo-endemism), restricted data set including only taxa endemic to Japan. 'neo' indicates neodendemic areas (those with an overabundance of short branches); 'paleo' indicates paleoendemic areas (those with an overabundance of long branches); 'mixed' indicates significantly endemic sites that have neither an overabundance of short nor long branches; 'super' indicates highly significantly endemic sites that have neither an overabundance of short nor long branches. For details, see Materials and Methods.

@@

Scatterplots of grid cell membership in (A) taxonomic or (B) phylogenetic bioregions arranged by mean annual temperature and annual precipitation. Points shown with partial transparency; darker areas indicate overlapping points. Bioregions not consisting of more than `r english2(bioregion_cutoff)` grid cells each are lumped into the "Other" category.

@@

Maps showing overlap of grid cells with significantly high biodiversity for the ferns of Japan and protected areas. Grid cells with black outlines indicate significantly high biodiversity. Biodiversity metrics include (A) taxon richness, (B) phylogenetic diversity (PD), (C) functional diversity (FD), and (D) phylogenetic endemism (PE). Significance of PD, FD, and PE assessed by a one-tailed test comparing observed values to a null distribution of 999 random values; for richness, grid cells in the top 5% considered highly diverse (see Materials and Methods).

@@

Maps showing overlap of grid cells with significantly high biodiversity for the ferns of Japan and distribution of Japanese deer (*Cervus nippon*). Grid cells with black outlines indicate significantly high biodiversity. Biodiversity metrics include (A) taxon richness, (B) phylogenetic diversity (PD), (C) functional diversity (FD), and (D) phylogenetic endemism (PE). Significance of PD, FD, and PE assessed by a one-tailed test comparing observed values to a null distribution of 999 random values; for richness, grid cells in the top 5% considered highly diverse (see Materials and Methods). Deer range data sources include 1978 survey, 2003 survey, and range estimated from model based on 2003 survey data. Deer ranges plotted in layers in ascending order (estimated, 2003, 1978) such that upper layers may obscure lower layers; however, deer ranges generally expanded from 1978 to estimated range, so very few sites are obscured.
